Stable Neo-Hookean Flesh Simulation

### 2019-11-29 LaTeX-Master-Vorlage/chapter/paper.tex
loooots of calculations

If the energy had rest stability $P_{D}(I)$ would resolve to zero. Unfortunately this is not the case here. In order to solve that problem the authors modified $(J-1)^{2}$ to $(J-\alpha)^{2}$:
\[
\Psi_{E} = \frac{\mu}{2}\left(I_{C}-3\right) +\frac{\lambda}{2}(J-\alpha)^{2}
\]
therefore resulting to:
\[
P_{E}(F) = \frac{\partial \Psi_{D}}{\partial F} \left[ \frac{\mu}{2}\left(I_{C}-3\right) +\frac{\lambda}{2}(J-\alpha)^{2} \right]
\]
\[
= \mu F + \lambda (\operatorname{det}(F)-\alpha)  \frac{\partial}{\partial F} \operatorname{det}(F)
\]
Solving for an alpha that satisfies $P_{E}(I)=0$ gives us $\alpha=1+\frac{\mu}{\lambda}$. Now $\Psi_{E}$ has to be changed accordingly:
\[
\Psi_{E} = \frac{\mu}{2}\left(I_{C}-3\right) +\frac{\lambda}{2}(J-1-\frac{\mu}{\lambda})^{2}
\]
\[
= \frac{\mu}{2}\left(I_{C}-3\right) - \mu\left(J-1\right) + \frac{\lambda}{2}(J-1)^{2} + \left(\frac{\mu}{\lambda}\right)^{2}
\]
Since constant disappear under differentiation this expression is functionally equivalent to 
\[
\Psi_{E} = \frac{\mu}{2}\left(I_{C}-3\right) - \mu\left(J-1\right) + \frac{\lambda}{2}(J-1)^{2}.
\]
Now one can notice that $\Psi_{E}$ looks very similar to $\Psi_{Neo}$. The difference is that we replaced $log(J)$ with $(J-1)$ in $\Psi_{E}$. Remember that $(J-1)$ is the first term in the taylor approximation of $log(J)$ at $J=1$:
\[
\sum_{n=0}^{\infty} = \frac{f^{(n)}(1)}{n!} (J-1)^{n} =
\]
\[
= (J-1) - \frac{1}{2} (J-1)^{2} + \frac{1}{3} (J-1)^{3} -\frac{1}{4} (J-1)^{4} + ...
\]

@@

\subsection{Meta-Stability under Degeneracy}
The final energy is
\begin{equation}\label{eq:stable_energy}
\Psi_{new} = \frac{\mu}{2}\left(I_{C}-3\right) + \frac{\lambda}{2}(J-\alpha)^{2} - \frac{\mu}{2}\left(I_{C}+1\right).
\end{equation}
With that adjustment the rest stability term shifts to $\alpha=1+\frac{\mu}{\lambda}-\left(\frac{\mu}{4}\right)\lambda$.

@@

\subsection{First Piola-Kirchhoff Stress (PK1)}
We start with PK1 for equation \ref{eq:stable_energy}:
\[
P(F) = \frac{\partial \Psi_{D}}{\partial F} \left[ \frac{\mu}{2}\left(I_{C}-3\right) + \frac{\lambda}{2}(J-\alpha)^{2} - \frac{\mu}{2}\left(I_{C}+1\right) \right]
\]

>>>>

If the energy had rest stability $P_{D}(I)$ would resolve to zero. Unfortunately this is not the case here. In order to solve that problem the authors modified $(J-1)^{2}$ to $(J-\alpha)^{2}$:
\[
\Psi_{E} = \frac{\mu}{2}\left(I_{C}-3\right) +\frac{\lambda}{2}(J-\alpha)^{2}
\]
therefore resulting to:
\[
P_{E}(F) = \frac{\partial \Psi_{D}}{\partial F} \left[ \frac{\mu}{2}\left(I_{C}-3\right) +\frac{\lambda}{2}(J-\alpha)^{2} \right]
\]
\begin{equation}\label{eq:pk1_unstable}
= \mu F + \lambda (\operatorname{det}(F)-\alpha)  \frac{\partial}{\partial F} \operatorname{det}(F)
\end{equation}

Solving for an alpha that satisfies $P_{E}(I)=0$ gives us $\alpha=1+\frac{\mu}{\lambda}$. Now $\Psi_{E}$ has to be changed accordingly:
\[
\Psi_{E} = \frac{\mu}{2}\left(I_{C}-3\right) +\frac{\lambda}{2}(J-1-\frac{\mu}{\lambda})^{2}
\]
\[
= \frac{\mu}{2}\left(I_{C}-3\right) - \mu\left(J-1\right) + \frac{\lambda}{2}(J-1)^{2} + \left(\frac{\mu}{\lambda}\right)^{2}
\]
Since constant disappear under differentiation this expression is functionally equivalent to 
\[
\Psi_{E} = \frac{\mu}{2}\left(I_{C}-3\right) - \mu\left(J-1\right) + \frac{\lambda}{2}(J-1)^{2}.
\]
Now one can notice that $\Psi_{E}$ looks very similar to $\Psi_{Neo}$. The difference is that we replaced $log(J)$ with $(J-1)$ in $\Psi_{E}$. Remember that $(J-1)$ is the first term in the taylor approximation of $log(J)$ at $J=1$:
\[
\sum_{n=0}^{\infty} = \frac{f^{(n)}(1)}{n!} (J-1)^{n} =
\]
\[
= \boldsymbol{(J-1)} - \frac{1}{2} (J-1)^{2} + \frac{1}{3} (J-1)^{3} -\frac{1}{4} (J-1)^{4} + ...
\]

@@

\subsection{Meta-Stability under Degeneracy}
The final energy is
\begin{equation}\label{eq:stable_energy}
\Psi_{new} = \frac{\mu}{2}\left(I_{C}-3\right) + \frac{\lambda}{2}(J-\alpha)^{2} - \frac{\mu}{2} \operatorname{log}\left(I_{C}+1\right).
\end{equation}
With that adjustment the rest stability term shifts to $\alpha=1+\frac{\mu}{\lambda}-\left(\frac{\mu}{4}\right)\lambda$.

@@

\subsection{First Piola-Kirchhoff Stress (PK1)}
We start with PK1 for equation \ref{eq:stable_energy}:
\[
P(F) = \frac{\partial \Psi_{D}}{\partial F} \left[ \frac{\mu}{2}\left(I_{C}-3\right) + \frac{\lambda}{2}(J-\alpha)^{2} - \frac{\mu}{2}\left(I_{C}+1\right) \right]
\]
\[
\stackrel{\text{eq.\ref{eq:pk1_unstable}}}{=} \mu F + \lambda (\operatorname{det}(F)-\alpha)  \frac{\partial}{\partial F} \operatorname{det}(F) - \frac{\partial}{\partial F} \left[\operatorname{log}\left(\operatorname{tr}(\mathrm{F}^{T}F)+1\right)\right]
\]
\[
= \mu F + \lambda (\operatorname{det}(F)-\alpha)  \frac{\partial}{\partial F} \operatorname{det}(F) - \mu F \frac{1}{\operatorname{tr}(\mathrm{F}^{T}F) + 1}
\]
\[
= \mu \left( 1 - \frac{1}{\operatorname{tr}(\mathrm{F}^{T}F) + 1}\right) F + \lambda(J-\alpha)\frac{\partial J}{\partial F}
\]

with $\alpha=1+\frac{\mu}{\lambda}-\left(\frac{\mu}{4}\right)\lambda$. For future use we write $\frac{\partial J}{\partial F}$ as cross products:
\[
\frac{\partial J}{\partial F} = \left[ \,f_1 \times f_2\, \bigg| \,f_2 \times f_0\, \bigg| \,f_0 \times f_1\, \right].
\]
